At a global scale, conservation of pollinators and herbivores between related plants varies widely across communities and between plant families - Supporting Information

### 2019-12-09 manuscript/reply_to_referees_2.tex

		\begin{refquote}
			Line 262. Your first sentence of results do not correspond with what follows. We will suggest you use most networks, or most herbivory networks and half pollination networks, or using the percentages you present in the discussion section.
		\end{refquote}

		\textbf{R:} We had some difficulty interpreting this comment but are guessing that the Referee is confused by the transition between the overall trend (more related plants have more similar interaction partners) and the variability of the trends within specific networks. To help understand this, note that the structure of the first few lines of the discussion parallels the first few lines of the results. First we introduce the overall result, and then we expand upon the details. We have edited lines 370-373 to make this clearer:

@@

		\end{quotation}

	17. Definition of community composition unclear

		\begin{refquote}
			Line 310. How was community composition measured? Is difficult to evaluate the quality of this result because you haven't described this methodology.
		\end{refquote}

		\textbf{R:} We define community composition as the set of plant species that make up a community, as described by the researchers constructing each network. For tractability, we have summarized community composition as the number of species in each plant family. We have added text to the methods to state this more explicitly.

@@

		Lines 224-233:

		\begin{quotation}
			Next, we examined the connection between our network-level observations
			and the number of species in each plant family present in each community.
			Specifically, we tested the hypothesis that
			varying relationships between phylogenetic distance and pairwise
			niche overlap are due to the different distributions 
			of families across networks. We defined the relationship between
			phylogenetic distance and niche overlap as the change in 
			log odds of two plants in a given network sharing an interaction 
			partner per million years of divergence (i.e., the slope $\beta_{distance}$ from the 
			regression of niche overlap against phylogenetic distance within
			a single network). We then related differences in this relationship
			to differences in the composition of the plant community 
			using a non-parametric permutational multi-variate 
			analysis of variance (PERMANOVA;~\citealp{Anderson2001}).
	    \end{quotation}

	18. Confusion about permutation methodology

		\begin{refquote}
			Minor comments on Results\\
			297-298 You permuted interactions or phylogenetic distances?
		\end{refquote}

		\textbf{R:} As stated in the methods, we permuted interactions. In statistical terms, the two approaches are equivalent, but we appreciate that this may not be obvious given that permutation approaches are not terribly common. We have rephrased the results to match the methods.

	19. Typo in Fig. 1 caption

@@

		\textbf{R:} We thank the Referee for pointing out this truly egregious typo, and have corrected it.

	20. Difference between minimum and maximum slopes not visible

		\begin{refquote}
			Fig 2. It is no clear for us. Minimum and maximum slopes obtained from 999 permutations are the same value?
		\end{refquote}

		\textbf{R:} As stated in the caption, the minimum and maximum slopes from the permutations are very close to 0. The clarify that they are not the same values, we now give the range of slopes (-1.34$\times10^{-12}$ to 9.19$\times10^{-13}$) as in the caption of Fig. 1. We hope that this is now clearer.

	21. Number of families unclear in line 328

@@

		\begin{refquote}
			Line  328: "...increasing phylogenetic distance in 12...", what is 12? the number of families?
		\end{refquote}

		\textbf{R:} The Referee is correct; 12 is indeed the number of families. We have revised the line to make this more explicit. Note that we have also corrected this line to match Table 1, which includes 14 significant families.

@@

		\begin{refquote}
			Table number seem to be erroneous as you first mention table 2 and then table 1.

			\smallskip

			Figure 3 is only referenced in the text when talking about herbivory networks but not for pollination networks.
		\end{refquote}

		\textbf{R:} We have reordered the tables and added a second reference to Fig. 3.

	23. Request for more evolution content

		\begin{refquote}
			Discussion\\
			General\\
			We suggest you include ideas about evolution and coevolution in networks in your discussion. It is important to recognize that network structure is in part a consequence of the evolutionary process and that we cannot think in the pairwise-coevolutionary framework as the only one modulating trait evolution in species rich assemblages.
			You state that the fact that the proportion of specialist species may explain differences between plant-pollination and plant-herbivore network patterns and you discuss the mathematical consequences of such difference but you should discuss the ecological and evolutionary causes and consequences of having higher specialization in pollination networks. This is also related with your methodological decision of excluding more specialized herbivores, isn't it?
		\end{refquote}

		\textbf{R:} We completely agree that, together with ecological processes and environmental filtering, evolution and coevolution are very important in structuring networks. However, since we do not have trait or genetic data for our networks, we cannot comment with any certainty on which of our results are due to trait plasticity or environmental influence and which are due to evolution. We therefore mention possible evolutionary and ecological explanations together. This mixture may have led the Referee to miss the evolutionary and coevolutionary ideas which are embedded throughout the discussion. We highlight some examples of these ideas below:

@@

		\end{quotation}

	24. Objection to claim of "broad support"

		\begin{refquote}
			338-339. You state We found broad support for the hypothesis that more closely-related pairs of plants have a higher degree of niche overlap. This is a very strong sentence that is not supported by your results. You found evidence in 55\% of plant-pollination networks (almost half of your dataset). In fact, it is interesting to note that even the slope is more pronounced in mutualistic networks you found higher support in herbivory networks, as a higher percentage of networks showed a tendency.
		\end{refquote}

		\textbf{R:} We found that more closely-related pairs of plants have greater niche overlap when considering all networks together, as well as in the majority of networks considered separetely. 
		Moreover, the number of networks displaying significant trends (56\% of the pollination networks and 64\% of herbivory networks) is much greater than we would expect to occur purely by chance. Putting all of this together, we contend that there is indeed broad (in the sense of 'general' or 'overall') support for our hypothesis. In case it is simply the synonymy between broad and general that has perplexed the Referee, we have revised this line to state ''We found \emph{general} support...''. We hope that this wording is less contentious when the overall trends and preponderance of within-network results are considered together.

		Nevertheless, we agree with the Referee that we do not have universal support for our hypothesis. This is why we provide the numbers of networks which did and did not support our hypothesis immediately after stating the oveerall trend. This allows readers to agree or disagree with our choice of words based on their interpretation of the facts.

		We are glad that the Referee finds the greater proportion of significant herbivory networks interesting. We also find the possibility of stronger conservation of interaction partners in herbivory networks intriguing. 
		With the unbalanced sample sizes of pollination and herbivory networks, however, we are somewhat reluctant to make much of the difference between 56\% and 64\%. We consider that the important point here is that networks are more likely than not to show decreasing niche overlap with increasing phylogenetic distance.

	25. Suggestion that low numbers of specialist herbivores are an artefact

@@

		\begin{refquote}
			351-352 The herbivory networks did not contain as many obligate specialists, but we note that many herbivorous insects are oligotrophs which consume only a few closely-related hosts (Novotny \& Basset, 2005; Yguel et al., 2011). This sentence is confuse because you have a subsample of herbivory networks and then this seems to be a by-product of your study design associated with your decision of removing networks that may show strong phylogenetic signal.
		\end{refquote}

		\textbf{R:} We must again point out that subsetting the herbivory networks as we have done was requested during an earlier round of review. We are therefore reluctant to reconsider this approach without a very good reason.

		Beyond the objection to the dataset, it appears that the Referee is claiming that oligotrophy rather than strict specialisation is an artefact of our dataset rather than a general feature of herbivory networks. Note, however, that~\citet{Novotny2005} addresses leaf-chewers as intermediate in their level of specialisation on particular families and emphasises that herbivores in general (regardless of guild) tend to consume a few closely-related hosts. They point out the relative rarity of strict specialists compared to specialists on species within a particular genus or family.~\citet{Brandle2006} also found insect herbivores were specialised on a particular genus but consumed multiple species within the genus. As~\citet{Brandle2006} focus on phytophagous insects specifically, we feel that this reference addresses our point more directly than~\citet{Yguel2011}. We have therefore replaced this reference and hope that this improved support will better demonstrate that the low levels of strict specialist herbivores in our dataset are not artefactual.

	26. Claims that congeneric species are not closely related

@@

		\begin{refquote}
			357-359 This suggests that conservation of interaction partners among closely related plants (e.g., congeners or members of the same subfamilies) is more important than phylogenetic signal from deeper within the phylogenetic tree. Congeneric species can be not closely related, please revise sentences like this one across the manuscript because you are confounding phylogeny with taxonomy.
		\end{refquote}

		\textbf{R:} We may have failed to grasp the essence of this comment, as it seems that the Referee is suggesting that plants in the same genus are generally less closely-related than plants in different genera. This is quite counter-intuitive. We agree that plants within some genera are more closely-related than plants within other genera, but because we always use phylogenetic distance in our analyses, these differences do not influence the slopes we observe. Here we are not comparing the divergence times of different genera but referencing the nested nature of phylogenies as a whole. Referring to genera and subfamiliees is intended as a guide for readers who may not be expert phylogeneticists and could appreciate a reminder that we are considering branches near the tips of a phylogenetic tree.

		In general, we believe that taxonomy is a reasonable proxy for phylogeny, and that two plants from within a genus will be more closely related than two plants in different genera. We are not aware of any evidence to the contrary, but are open to exploring this viewpoint if the Referee would like to provide some citations. In the meantime, we have opted not to change our text.

	27. Request to discuss results in terms of intimacy

@@

		\begin{refquote}
			361-365. How interaction intimacy may explain your results? Please, discuss your results in light of the interplay between interaction type (pollination, herbivory) and intimacy (see Hembry et al. 2018).
		\end{refquote}

		\textbf{R:} We do not have information about the intimacy of different interactions within our dataset and are reluctant to speculate about what the effects of intimacy might be without data. Both leaf-chewing herbivory and pollination are generally low-intimacy interactions~\citep{Astegiano2017}, but there may still be variation in intimacy within these groups. Without more detailed information, that is as far as we can comment without pure speculation.

		It is also difficult to compare our work to that of~\citet{Hembry2018} as their small and extremely intimate system is quite different from our larger, more diverse dataset. In particular, our pollination and herbivory networks generally describe different systems, so we cannot test whether reciprocal specialisation is more common for plants which interact with the same animals as pollinators and herbivores. We agree that this would be interesting, but it is a question best left for future work and a more targetted data set.

		Given all of the above, we do not believe that a detailed discussion of intimacy fits well with our discussion. We do want to keep this idea in readers heads, however, and have added a brief description of the idea in lines (lines 443-454):

@@

		\begin{quotation}

			Selection to avoid 
			competition and restrict numbers of interaction partners may lead to
			more intimate or specialised interactions~\citep{Ponisio2017}. 
			This is particularly the case in highly intimate interactions, where both partners may specialise~\citep{Hembry2018}.
			Past selection to avoid competition is 
			consistent with the relatively high proportion of extreme specialists we
			observed in the pollination networks.

@@

			\smallskip

			p. 5, l. 69-71 « In either case, dissimilarity (…). » This sentence helped me to understand why it is important to look at unshared interactions. To be better showcased ?

		\end{refquote}

		\textbf{R:} The number of shared and unshared interactions are indeed both dependent variables included in the analysis. The number of shared variables is the key variable, but the number of unshared interactions is also important as it indicates how extraordinary a particular number of shared interactions is. The binomial process incorporates both quantities; converting the numbers of shared and unshared interactions to a proportion and weighting the observations by the total number of interactions. We thank the Referee for pointing out text in the introduction which clarified the purpose of including unshared interactions, and have used it as the basis for improving the methods. We have expanded the beginning of this section to explain the logic of our modelling approach in more detail, and a brief appendix which shows how a tuple can be given as input in a regression model in R.

@@

		lines 130-141:

		\begin{quotation}

			We calculated niche overlap for each pair of plants $i$ and $j$ based on the number of shared and unshared interaction partners ($M_{ij}$, $U_{ij}$, respectively). 
			The number of unshared interaction 
			partners gives valuable information about cases where, for example, 
			closely-related plants may have experienced disruptive selection, leading to weaker phylogenetic signal. 
			The sum $M_{ij} + U_{ij}$ indicates the amount of information  provided by each pair of plants: a pair of generalists which share most of their interaction partners gives a stronger indication of phylogenetic signal than a pair of extreme specialists with one common interaction partner.

			Together, $M_{ij}$ and $U_{ij}$ give a Jaccard index ($J_{ij}$) describing 
			the proportion of shared interactions. $J_{ij}$ is defined: 
			\begin{equation}
			J_{ij} = \frac{M_{ij}}{U_{ij}+M_{ij}} ,
			\end{equation}
			where $M_{ij}$ is the set of \emph{mutual} (shared) interaction partners and $U_{ij}$ the set of unshared interaction partners for plants $i$ and $j$ (see \emph{Supplemental Information 2} for R implementation).

### 2019-12-09 manuscript/reply_to_referees_2_dbs.tex

\begin{letter}{\bf Dr. Jana Vamosi\\
               Editor\\
               Proceedings of the Royal Society B\\
               6-9 Carlton House Terrace\\
               London, UK\\
               SW1Y 5AG\\
                }

\opening{Dear Dr. Vamosi:}

	We are pleased to submit a revised version of our manuscript, NPH-MS-2019-30803. In response to a suggestion from Referee 3, we have re-titled it "". We have also taken care to revise our methods section in response to the many helpful suggestions from Referee 4, and hope that our approach is now clearer. Finally, we have expanded the discussion to include some additional concepts suggested by Referees 2 and 4, and a possible application of our research suggested by Referee 3.

	Given the difference of opinion between Referees 1, 3, and 4 and Referee 2, we have prioritised adjusting the manuscript according to the majority view. We must also admit to having some difficulty parsing a number of Referee 2's comments in order to find what precisely was being asked. This may be partly because this review came from several people - the Referee refers to themselves as 'we' several times, and the writing appears to be more than usually variable within their comments. These difficulties mean that we may not have followed as many of Referee 2's suggestions as we have for the other Referees. Nevertheless, we do appreciate their time and effort in offering such extensive feedback and have taken care to address each of Referee 2's comments to the best of our abilities in the hope of at least clarifying our perspective.

@@

	\smallskip

	In what follows we share with authors our specific comments expecting that they will help to re-think the manuscript and get a stronger contribution.

	\end{refquote}

	The Referee seems to view our basic question and analyses positively, but is rather critical of our writing in terms of logical, clarity, and style.
	%Some of these criticisms seem to reflect a rather hasty reading of the manuscript, as
	There are points where the Referee asks for analyses or ideas to be included which we felt already appeared in the text.
	In these cases, we point to the areas in question and have tried to make these connections more apparent.
	In a few further cases, we were not fully able to identify the core of the Referee's objections. We have attempted to address each of the Referee's comments in detail below (preceded by \textbf{R:}). Wherever possible, we have clarified our text in response to the Referee's comments. In particular, we now define community composition more explicitly, have revised the discussion to be more explicit about whether we are referring to overall or within-network trends, and have removed specific phrases that the Referee found objectionable \emph{prima facie}. We hope that these changes and our response will clarify the focus and scope of our analyses.

@@

		\begin{refquote}

		Finally, the text needs English revision by the authors as we feel that some ideas are not clearly stated because of the way they are presented to readers.

		\end{refquote}

		\textbf{R:} 
		%As Referees 1 and 3 note, our English is scrupulously correct. Of course technical correctness does not necessarily imply clarity of expression, and we apologise if our choice of vocabulary has obfuscated some of the nuances of the manuscript. We have endeavoured to clarify the manuscript as the Referee suggests.
		We are sorry the Referee found the text less clear than we would have desired. We have gone through the latest version very carefully with a focus on the clarity of the text.

@@

	2. Title lacks clarity

		\begin{refquote}
		Specific comments\\
		Title\\
		Your title still lacks clarity and does not reflect the main message you state at the beginning of your discussion (in the first sentence of it you state that you found broad support for the hypothesis that more closely related plants tend to have more niche overlap). We feel that this reflects lack of logical consistency across your manuscript, so re-thinking it should help to define your title.
		\end{refquote}

		\textbf{R:} We have revised the title following a more detailed suggestion by Referee 3 and hope that the new title is a better reflection of the manuscript as a whole.

@@

	3. Summary too methodologically-oriented in general

		\begin{refquote}
			Summary\\
			General comments\\
			Your summary is too methodologically-oriented. In fact, when we were invited to be reviewers of your manuscript and received your abstract we thought that your paper represented a methodological contribution and it is not. After reading the comments that former reviewers sent you, your abstract seems to correspond to an older version of your manuscript. The thing is that by presenting an abstract that is methodologically-oriented when in fact you are not innovating in this sense, and having an introduction and a discussion that lack such methodological issue and are clearly more biologically-oriented can be read as that your work lacks focus.
		\end{refquote}

		\begin{refquote}
			Your 2nd paragraph is too technical: which is the biological meaning of it? Why are you going to compare pollination and herbivory networks? Why your datasets are so unbalanced? Why are you considering a wide range of pollination networks and a narrow one for herbivory networks? Why you consider shared and unshared partners? Your first point in the abstract doesn't introduce a methodological problem to be solve. (...) "and whether this relationship varies with the composition of the plant community"? What does it mean?
		\end{refquote}

		\textbf{R:} We regret that the Referee found our summary too methodologically-orientated. We also note that Referee 4 has requested that we include further methodological details in the summary. To balance these out, we no longer emphasise the methodological novelty of our study but have added the greater detail requested. We also note, however, that the extremely tight word limit for the summary does not allow us to explain why we have unbalanced numbers of pollination and herbivory networks. This information is contained in the Methods.

@@

	4. Mis-understanding of purpose and scope of within-family analyses

		\begin{refquote}
		Your abstract also evidences your confusion with phylogenetic issues and taxonomic ones. For instance, your hypothesis is that more closely related plants will share more pollinators and herbivores than less closely related. Then, why searching for different relationships within families? This decision is completely arbitrary is one of the weakest point of the manuscript in general.
		\end{refquote}

		\textbf{R:} The Referee is correct about our hypothesis but it appears that our earlier version lead them to believe that we are \emph{only} searching for conservation of niche overlap within families. In fact, point 2 of the summary lists three separate analyses: testing for relationships between phylogenetic distance and partner overlap in \emph{all pairs of plants in a network, regardless of family}, testing whether the slopes of these whole-network relationships are related to the composition of the plant community in each network, and, as a supplement to these analyses, testing whether the slopes of these relationships differ if we consider only pairs of plants within the same family. We now number these three different analyses to avoid any further confusion.

		In this context, checking for different relationships within families is similar to checking for different relationships between networks - an overall trend can mask a great deal of variability, and we wanted to make sure this variability was identified as best possible. We chose families as the taxonomic level for further analysis because many plant families are quite diverse, both in terms of numbers of species and in terms of phenotypes/interaction partners (see e.g., Wilson on plants and insect/bird pollinators). Within a single family, plants can show evidence of adaptive radiations, heterogeneous selection, both, or neither. The Referee themself points out that some families can show both bird and bee pollination syndromes (see response \#8), and we can also point to papers such as Bernhardt 2000 and Johnson \& Jurgens 2010 which address trait lability, convergent evolution, and adaptive radiation. These different possibilities mean that it is not clear whether all families will show phylogenetic conservation of interaction partners. 
		As we seem to have failed in making this point clearly in the earlier version, we have added a summary of this explanation to the methods.

@@

		\begin{quotation}

			Finally, we compared the breakdown of niche overlap in different plant families.
		    Within-family genetic and trait diversity can be high due to adaptive radiations, heterogeneous selection, and other influences on different species. 
		    Plant families offer a reasonable balance between collecting enough species to identify meaningful trends and maintaining a tractable number of analyses. 
		    They are therefore the best taxonomic level to investigate phylogenetic conservation in more detail across our large dataset.

		\end{quotation}

		As we are not searching for differences \emph{between} communities at the family level, but rather at all levels within the angiosperms, a number of the Referee's comments did not seem to directly apply. I their brevity, it is possible that we were unable to capture the Referee's principle argument, so we list these below in case they prefer greater clarification going forward.

@@

		\begin{refquote}
			Line 318. Within-family conservation of niche overlap. Your result is almost expected so we think is important to justify biologically why you decided to look at the family level.
		\end{refquote}

	5. Comments about summary point 4

		\begin{refquote}
		4st paragraph "Considering factors affecting the dominant plant families within
		a community may be the key to understanding the distribution of interactions." So, relationships are more functional? Why focusing on plant families? we are not sure the logic of your thoughts can be followed (can the reader reach this conclusion? is it ok? we mean, if there are other eco-evolutionary processes determining species interactions why focusing in the dominant plant families would be informative? I feel the way this last paragraph is written isn't clear enough and is your main paragraph.
		\end{refquote}

		\textbf{R:} Apart from the Referee's objection to plant families as units for detailed analysis (see response \#4), this comment seems to demonstrate uncertainty about how we defined the dominant plant families in a community. Note that we do not mean to imply any functional argument here, as our manuscript does not address functionality. Rather, by 'dominant', we mean 'most species-rich in the focal community'. In order to avoid future confusion, we now replace 'dominant families' with 'species-rich groups'. We hope that this makes it clear that we are advocating researchers take a finer-scale perspective on phylogenetic signal in ecological networks.

@@

		\begin{quotation}
		    \item The variety of relationships between phylogenetic distance and partner overlap in different plant families likely reflects a comparable variety of ecological and evolutionary processes. Considering factors affecting particular species-rich groups within a community may be the key to understanding the distribution of interactions.
		\end{quotation}

	6. Complaint about keywords absent from the abstract

		\textbf{R:} The abstract/summary is under strict word limits, and we did not feel that inserting each keyword without a clear purpose could justify the elimination of other material.
		%Given the Referee's confusion regarding our analyses, we are more convinced than ever that our decision to omit some keywords in favour of spending more words explaining our methodology was correct.
		As we do not directly test pollination or defensive syndromes, we have removed these keywords from the list. In response to the Referee's further objections to the syndrome literature, below, we have also removed these terms from the introduction.

	7. The focus of the introduction

@@

	7. The focus of the introduction

		\begin{refquote}
		Introduction\\
		General. You focus on the compromise between pollination and herbivory interactions but then you do not use this approach in your analyses.
		\end{refquote}

		\textbf{R:} Potential tradeoffs between encouraging interactions with pollinators and discouraging herbivores are just one of the possible reasons why networks may not display the expected relationship between relatedness and niche overlap. Note that we also propose several others in the same paragraph where trade-offs appear, including convergent evolution or selection to avoid pollen dilution. We therefore disagree with the Referee's perception that out primary focus is the compromise between pollination and herbivory.
		% It is beyond the scope of this manuscript to test all possible reasons why closely-related plants might not share interaction partners.
		This material is intended solely as background for readers who may not be familiar with arguments against the phylogenetic conservation of interaction partners. We have reviewed the text in question to reassure ourselves that this is the tenor of our discussion.

	8. Disagreement with any link between syndromes and conservation of interaction partners

@@

		\begin{refquote}
			2nd paragraph: your reasoning is not clear for us. Syndromes imply the convergence of phenotypic traits into one common set of traits because of their functionality in increasing fitness (because of the selection pressures imposed by functional groups of pollinators that can or cannot be closely related). Even if traits are heritable, if many unrelated groups converge into one functional group of interaction partners, why you may expect more similarity among closely related species? On the other hand, can we expect modular structures based on your reasoning? Then, how you explain the high incidence of nested structures in both mutualistic and antagonistic networks? In fact, what has been proposed for coevolution in mutualistic networks is the convergence of species traits to those of the species forming the core (see Guimaraes et al 2017, Nuismer et al. 2018). In antagonistic networks your line of reasoning may apply, but this will clearly depend on the intimacy of your network as most herbivory networks tend to show nested structures too. Your reasoning is based on pairwise coevolution and does not incorporate ideas of evolution and coevolution in networks, which may completely alter your predictions about niche overlap.
		\end{refquote}

		\begin{refquote}
			Lines 65-65. You wrote: Unrelated plants might also converge upon similar phenotypes, attracting a particularly efficient or abundant pollinator (Ollerton, 1996; Wilson et al., 2007; Ollerton et al., 2009; Ibanez et al., 2016). This is exactly our point: pollination syndromes may reflect trait convergence among unrelated species.
		\end{refquote}

		\textbf{R:} As the Referee notes, we do address the possibility of convergence in our introduction. We do not make any claim as to whether the putative pollination syndromes actually reflect plants with common sets of pollinators (the evidence we are aware of is rather mixed). Since the Referee appears to object to this idea (which we nevertheless note is quite common in the literature surrounding phylogenetic conservation of interactions), and because syndromes do not form a major part of our analysis, we have removed it as a keyword and rephrased our introduction so that it now no longer references pollination syndromes. Hopefully this will help readers to evaluate our manuscript on its own merits rather than those of the syndrome concept.

@@

		\begin{quotation}

			In mutualistic networks, animals often show a stronger phylogenetic signal in their partners than do plants~\citep{Rezende2007a,Chamberlain2014,Rohr2014,Vamosi2014,Lind2015,Fontaine2015} (but see~\citet{Rafferty2013} for a counterexample). In antagonistic networks, however, actively-foraging consumers tend to show less phylogenetic signal than their prey~\citep{Ives2006,Cagnolo2011,Naisbit2011,Fontaine2015}. In part, this may be related to different degrees of interaction intimacy (dependence of one partner on another), which appears to contribute to network structure in mutualistic, but not antagonistic, networks~\citep{Guimaraes2007,Ponisio2017}.

		\end{quotation}

		In addition to the above, we have added another brief discussion of intimacy in the discussion (see response \#28)

	10. Criticism of dataset %changes required by previous reviewers

@@

		\begin{refquote}
		Methods\\
		Dataset\\
		Several networks can be reviewed in the literature or are available in different websites. Why authors decide not to consider several plant-herbivore networks but have no filter to separate plant-pollinator networks? The reason of why focusing in plant-pollinator and plant-herbivory networks is not clear for us as well why authors choose to select just one kind of herbivory interaction and as a consequence have a highly unbalanced design. Such decision seems to be crucial as it may modulate the results and conclusions they achieve. By eliminating the herbivory interactions that are more phylogenetically constrained their result that pollination interactions may be more conserved than herbivory interactions seems to be a by-product of such decision.
		\end{refquote}

		\textbf{R:} We included all herbivory networks we could find when we began this project, and only restricted our selection of herbivory networks in response to a previous round of review. Without more details regarding why (or if) the Referee believes that the herbivory networks we removed should be included, we have opted to continue following that earlier feedback. We would have appreciated specific tips pointing us toward additional herbivory networks, but lacking this information we concluded that  conducting a further search for additional networks and repeating our analyses was un-viable within the timeframe given to respond to this review.

	11. Request to change "insects consuming leaves" to "chewing insects"

@@

		\begin{refquote}
			Lines 93 to 96. We think that sap-sucking, leaf mining, and galling insects are also insect consuming leaves. Maybe you could change "insect consuming leaves" by "chewing insects"
		\end{refquote}

		\textbf{R:} The term "insects consuming leaves" was recommended by an earlier reviewer, but we agree that leaf mining also constitutes leaf consumption (this is not necessarily the case for sap-sucking and galling, which is less leaf-specific). We have changed these lines as suggested.

	12. Recommendation to continue using Jaccard dissimilarity, binomial regression

@@

		\begin{refquote}
			Measuring niche overlap\\
			Why you used absolute numbers to measure shared and unshared pollinators and not the Jaccard index? Or, instead, why you did not use a binomial regression considering the absolute number of the whole set of pollinators that can be shared ? You should use generalized linear models with a binomial distribution considering the total number of pollinators and shared pollinators to give more weight to those species sharing more pollinators in a larger sample (generalists s for instance). It is not clear for us if your analysis considers the full number of species over which you obtain the percentage of shared species.
		\end{refquote}

		\textbf{R:} We apologize for any confusion here, as we did in fact use a Jaccard index, as stated in the first  sentence under the sub-heading \textbf{Calculating niche overlap between communities} in the previous revision. This line read as follows (emphasis added): 
		\begin{quotation}
		We calculated niche overlap for each pair of species within a community \emph{using a Jaccard index} to describe the number of shared interaction partners, augmented with the number of interaction partners which were not shared.
		\end{quotation}

		The Jaccard index is calculated using the number of shared and un-shared interaction partners for a pair of plants, as stated in equation 1. We also did use a generalised linear model with binomial error distribution, as stated in the \textbf{Statistical analysis} section. We chose this methodology for exactly the reasons the Referee suggests, to give more weight to generalists sharing many interaction partners. This is stated in lines 138-141 and lines 148-154 (quoted below). Note that we have revised these lines somewhat in response to a suggestion from Referee 4, so they do differ somewhat from the previous version. We are glad that the Referee agrees with our choice in methodology.

@@

		As stated in the section on phylogenetic data, we excluded comparisons involving plants for which we could not assign a binomial names (and therefore could not obtain phylogenetic distances) and comparisons between non-angiosperms due to our coarse estimates of their ages. This information appeared in lines 107-110 and 118-120 of the previous version and lines 112-115 and 122-124 of the current version.

	13. Request to include plant species as a fixed effect

		\begin{refquote}
			176-178. Why you do not consider using plant species as another fixed factor to break the lack of independence? This is because generalist species may have more weight in your analyses than other species. It would be interesting to see how your results differ from an analysis considering such approach.
		\end{refquote}

		%DBS: I think your interpretation is incorrect here. I believe that they are referring to the fact that species with many interactions have a greater chance of "strong" overlap than species with few interactions. Either way though, I don't think this can be operationalized because each pairwise overlap value is tied to two species and not one (and that isn't tractable, in a way that I can think of...).

		\textbf{R:} It sounds as though the Referee would like us to include plant species as a predictor in our regressions. Due to the fact that species generally appear in few networks (many in only a single network), this would result in near singularity of our models. We would therefore be completely unable to observe any patterns as species identity would explain nearly all variation in niche overlap. If the Referee is referring to a potential effect of network size, we did in fact test this (see equation 4 and description). If the Referee did not mean either of these possibilities, we apologise but are unable to understand this comment.

	14. Request to include connectance

@@

		\begin{refquote}
			198-209. Why did you decide to control just for network size and do not consider network connectance? You provide methodological information to explain your decision but there is no biological argument explaining why network size may influence the relationship between phylogenetic relatedness and niche overlap.
		\end{refquote}

		\textbf{R:} Our main reason for including network size as a potential effect was methodological rather than biological - slopes for smaller networks are based on smaller sample sizes and therefore may be less robust. In contrast, we were unable to determine among ourselves what the methodological or biological arguments would be for including connectance as a predictor
		We also note that the manuscript is already quite full, so including these new analyses would require us to remove which we and other Referees have regarded as more important. Without a justification from the Referee as to why connectance should affect pairwise niche overlap, we have opted not to add this new thread to the manuscript.
		% DBS: This probably isn't true. If connectance were 0 there would be no overlap and if it were 1 overlap would be perfect. They probably think it sets a useful baseline. (?)

	15. Confusion about motivation for community composition analyses

		\begin{refquote}
			Line 210 Linking network level trends and community composition
